---
title: "FinalProject on Education Data"
author: "Lokesh Babu Rayadurgam"
date: "1 April 2019"
output: html_document
---

#I preferred this data due to below scenario:
#Education is an important medium of acquiring essential knowledge and skills. 
#It is more than just learning from books. It is an effort of the older generation to transfer their life wisdom to their offspring. 
#Once the project is at final stage,I will be able to explain the use of data extracting, formatting of the data and accessing with different packages.

```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)

datalink <- read.csv("https://raw.githubusercontent.com/loki825/FinalProject/master/Most-Recent-Cohorts-Scorecard-Elements.csv",header=TRUE, sep=",")
data <- data.frame(datalink)
#data
#data = data.dropna(how='any',axis=0)
#names(data)
data1<-data[1:8]
data2<-data[86:95]
datafinal<-cbind(data1,data2)
datafinal<-datafinal[1:500,]
sam<- grepl("UGDS_WHITE",names(datafinal))
datafinal[sam]<-lapply(datafinal[sam], function(x) replace (x,x %in% "NULL", NA))
datafinal
any(is.na(datafinal))
datafinal<-data.frame(na.omit(datafinal))

any(is.na(datafinal))

datafinal$Undergrads<-as.numeric(datafinal$UGDS)
datafinal$ug_white<-as.numeric(datafinal$UGDS_WHITE)
datafinal$ug_Asian<-as.numeric(datafinal$UGDS_ASIAN)
datafinal$ug_Black<-as.numeric(datafinal$UGDS_BLACK)
datafinal$ug_unkn<-as.numeric(datafinal$UGDS_UNKN)

ggplot(datafinal, aes(x=Undergrads,y=ug_white))+geom_point()+geom_smooth(method=lm,se=FALSE, color="black")
values<-lm(ug_white~Undergrads,data=datafinal)
coef(values)
summary(values)
datafinal$predictedValues<-predict(values)
datafinal$residualValues<-residuals(values)
#plotting  linear regression and residual values 
ggplot(datafinal,aes(x=Undergrads,y=ug_white))+geom_smooth(method=lm,se=FALSE,color="grey")+geom_segment(aes(xend=Undergrads,yend=predictedValues),alpha=0.2)+geom_point(aes(color=abs(residualValues)))+scale_color_continuous(low="red",high="blue")+guides(color=FALSE)+geom_point(aes(y=predictedValues),shape=1)
theme_bw()

```

```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)

datalink <- read.csv("https://raw.githubusercontent.com/loki825/FinalProject/master/Most-Recent-Cohorts-Scorecard-Elements.csv",header=TRUE, sep=",")
data <- data.frame(datalink)
#data
#data = data.dropna(how='any',axis=0)
#names(data)
data1<-data[1:8]
data2<-data[86:95]
datafinal<-cbind(data1,data2)
datafinal<-datafinal[1:500,]
sam<- grepl("UGDS_WHITE",names(datafinal))
datafinal[sam]<-lapply(datafinal[sam], function(x) replace (x,x %in% "NULL", NA))
datafinal
any(is.na(datafinal))
datafinal<-data.frame(na.omit(datafinal))

any(is.na(datafinal))

datafinal$Undergrads<-as.numeric(datafinal$UGDS)
datafinal$ug_white<-as.numeric(datafinal$UGDS_WHITE)
datafinal$ug_Asian<-as.numeric(datafinal$UGDS_ASIAN)
datafinal$ug_Black<-as.numeric(datafinal$UGDS_BLACK)
datafinal$ug_unkn<-as.numeric(datafinal$UGDS_UNKN)

ggplot(datafinal, aes(x=Undergrads,y=ug_Asian))+geom_point()+geom_smooth(method=lm,se=FALSE, color="black")
values1<-lm(ug_Asian~Undergrads,data=datafinal)
coef(values1)
summary(values1)
datafinal$predictedValues1<-predict(values1)
datafinal$residualValues1<-residuals(values1)
#plotting  linear regression and residual values 
ggplot(datafinal,aes(x=Undergrads,y=ug_Asian))+geom_smooth(method=lm,se=FALSE,color="grey")+geom_segment(aes(xend=Undergrads,yend=predictedValues1),alpha=0.2)+geom_point(aes(color=abs(residualValues1)))+scale_color_continuous(low="red",high="blue")+guides(color=FALSE)+geom_point(aes(y=predictedValues1),shape=1)
theme_bw()
```

```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)

datalink <- read.csv("https://raw.githubusercontent.com/loki825/FinalProject/master/Most-Recent-Cohorts-Scorecard-Elements.csv",header=TRUE, sep=",")
data <- data.frame(datalink)
#data
#data = data.dropna(how='any',axis=0)
#names(data)
data1<-data[1:8]
data2<-data[86:95]
datafinal<-cbind(data1,data2)
datafinal<-datafinal[1:500,]
sam<- grepl("UGDS_WHITE",names(datafinal))
datafinal[sam]<-lapply(datafinal[sam], function(x) replace (x,x %in% "NULL", NA))
datafinal
any(is.na(datafinal))
datafinal<-data.frame(na.omit(datafinal))

any(is.na(datafinal))

datafinal$Undergrads<-as.numeric(datafinal$UGDS)
datafinal$ug_white<-as.numeric(datafinal$UGDS_WHITE)
datafinal$ug_Asian<-as.numeric(datafinal$UGDS_ASIAN)
datafinal$ug_Black<-as.numeric(datafinal$UGDS_BLACK)
datafinal$ug_unkn<-as.numeric(datafinal$UGDS_UNKN)

ggplot(datafinal, aes(x=Undergrads,y=ug_Black))+geom_point()+geom_smooth(method=lm,se=FALSE, color="black")
values2<-lm(ug_Black~Undergrads,data=datafinal)
coef(values2)
summary(values2)
datafinal$predictedValues2<-predict(values2)
datafinal$residualValues2<-residuals(values2)
 
ggplot(datafinal,aes(x=Undergrads,y=ug_Black))+geom_smooth(method=lm,se=FALSE,color="grey")+geom_segment(aes(xend=Undergrads,yend=predictedValues2),alpha=0.2)+geom_point(aes(color=abs(residualValues2)))+scale_color_continuous(low="red",high="blue")+guides(color=FALSE)+geom_point(aes(y=predictedValues2),shape=1)
theme_bw()
```

```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)

datalink <- read.csv("https://raw.githubusercontent.com/loki825/FinalProject/master/Most-Recent-Cohorts-Scorecard-Elements.csv",header=TRUE, sep=",")
data <- data.frame(datalink)
#data
#data = data.dropna(how='any',axis=0)
#names(data)
data1<-data[1:8]
data2<-data[86:95]
datafinal<-cbind(data1,data2)
datafinal<-datafinal[1:500,]
sam<- grepl("UGDS_WHITE",names(datafinal))
datafinal[sam]<-lapply(datafinal[sam], function(x) replace (x,x %in% "NULL", NA))
datafinal
any(is.na(datafinal))
datafinal<-data.frame(na.omit(datafinal))

any(is.na(datafinal))

datafinal$Undergrads<-as.numeric(datafinal$UGDS)
datafinal$ug_white<-as.numeric(datafinal$UGDS_WHITE)
datafinal$ug_Asian<-as.numeric(datafinal$UGDS_ASIAN)
datafinal$ug_Black<-as.numeric(datafinal$UGDS_BLACK)
datafinal$ug_unkn<-as.numeric(datafinal$UGDS_UNKN)

ggplot(datafinal, aes(x=Undergrads,y=ug_unkn))+geom_point()+geom_smooth(method=lm,se=FALSE, color="black")
values3<-lm(ug_unkn~Undergrads,data=datafinal)
coef(values3)
summary(values3)
datafinal$predictedValues3<-predict(values3)
datafinal$residualValues3<-residuals(values3)
#plotting  linear regression and residual values 
ggplot(datafinal,aes(x=Undergrads,y=ug_unkn))+geom_smooth(method=lm,se=FALSE,color="grey")+geom_segment(aes(xend=Undergrads,yend=predictedValues3),alpha=0.2)+geom_point(aes(color=abs(residualValues3)))+scale_color_continuous(low="red",high="blue")+guides(color=FALSE)+geom_point(aes(y=predictedValues3),shape=1)
theme_bw()
```

